\section{Introduction}
The backbone of the internet infrastructure is controlled by cloud compute providers that process and store essentially the entire world's data.

While these centralized compute providers work well enough for most tasks, they suffer from the inherent weakness of a large trusted corporate conglomerate.

The main issue being cost and centralization, making a global decentralization network not truly possible with these providers. With a handful of cloud providers gaining more share each year, it will lead to much higher prices for compute, which, in turn, decreases the services able to operate.

With centralization, the need for redundancies also spreads, which increases costs and resources.
These weaknesses can be avoided by utilizing spare unused compute across the globe.

OctaSpace takes a distinct approach to building a scalable distributed compute system, which presents itself to compute users as a unified, coherent entity. This innovative method enables users to start renting Octa Nodes seamlessly, in a matter of minutes.

It's essential to have the system with unified interfaces and coherent behavior, providing a single entry point for the end-users' interactions similar to how cloud providers operate today.

OctaSpace is a distributed cloud platform to implement services built on top of hardware provided by decentralized users.

With OctaSpace, you can harness the power of CPU, GPU, storage, and traffic resources from Octa nodes across the world to tackle compute-heavy tasks.

By utilizing your spare hardware, it's possible to generate income by acting as a host and renting out your CPU/GPU or traffic.

The hardware required for this can range from basic, low-performance devices or inexpensive VPS to advanced mining rigs and carrier-grade servers located within data centers.

OctaSpace's initial goals:

\begin{itemize}
    \item Utilize a powerful of Hybrid 51\% attack proof blockchain to increase transparency.
    \item Provide easy to use interface for describing nodes and executing tasks and marketplace for renting computer focusing on GPU instances
    \item Provide infrastructure to deploy applications and databases mostly close to end users
    \item Implement a VPN marketplace using popular VPN technologies
    \item Implement distributed data storage and use it as a backbone for CDN service
    \item Increase OctaSpace accessibility globally
\end{itemize}

The sort of tasks the project focused on:

\begin{itemize}
    \item Machine Learning
    \item CGI rendering
    \item Digital image processing
    \item Scientific modeling
    \item Data storing and distributing
    \item VPN technologies
    \item Other tasks/fields which require massive computation power to get be solved
\end{itemize}
