\section{Reputation}

Reputation is an entity which consists of several values and represents the quality of the user's nodes.
It also helps to detect the non stable or malicious nodes,
increases the efficiency of the node selection algorithm and
affects the total reward amount.

Reputation is calculating on the daily basis consists of the following parameters:

\begin{itemize}
    \item Uptime (U) - the mean value of the nodes uptime
    \item Completed tasks (C) - the percentage of completed tasks
\end{itemize}

More parameters may be added if necessary.

The common reputation formula looks like:

\[
    R = \frac{\sum(U, C, ...)}{\vert{N}\vert}
\]

Where \textbf{N} is amount if items used in calculation.
The final value of the reputation is calculated for the 30 days period.

\subsection{Uptime}

Uptime is the measure of the uninterrupted time that a node system experiences.

We use the mean value of the uptime - sum of uptime of all users nodes divided by nodes amount.

\[
    U = \frac{\sum(u) / 2592000}{N}
\]

Where \textbf{u} is an uptime of the specific node, \textbf{2592000} is amount of seconds in 30 days and \textbf{N} is the total amount of nodes which are in online state.

\subsection{Completed tasks}

\[
    C = \frac{C}{N / 100}
\]

Where \textbf{C} is an amount of the completed tasks and \textbf{N} is the total amount of tasks accepted by the user's nodes.

\subsection{Examples}

User has 3 nodes - node A, node B and node C. During the last 30 days these nodes were online the following amount of seconds:

\begin{itemize}
    \item A - 2246400 seconds, 4 days downtime
    \item B - 1987200 seconds, 7 days downtime
    \item C - 2505600 seconds, 1 day downtime
\end{itemize}

According the to values above the mean uptime will be:

\[
    U = \frac{(2246400 + 1987200 + 2505600) / 2592000}{3} = 0.86 * 100 = 86\%
\]

Also these nodes accepted 743 tasks and 345 tasks were succesful, others one are canceled or failed or expired.

So to calculate the percent of completed task we apply the following formula:

\[
    C = \frac{345}{743 / 100} = 46.43\%
\]

The final reputation value will be:

\[
    R = \frac{86 + 46.43}{2} = 66.21\%
\]
