\section{Staking}
\label{sec:staking}

To incentive interest of holding the staking mechanism is introduced.

Using it people who locked some amount of coins and run node is rewarded.

There are requirements which need met to activate staking:

\begin{itemize}
    \item Collateral - 100\_000 OCTA
    \item Node reliability for the last 30 days $\ge$ 75\%
    \item Node must be verified
\end{itemize}

To start staking it's necessary to have the address wallet with enough balance and link it to existing node.
Reward will be come to the wallet provided.

If system detect balance less than collateral staking will be disabled for such wallet-node pair for
several rounds.

\subsection{Reward distribution scheme}

The billing period is 1 week (every 7 days).

Let's assume that block time is always 15 seconds then the following amount of blocks would be mined:

\begin{itemize}
    \item 1 minute - 4
    \item 1 hour - 240
    \item 1 day - 5760
    \item 7 days - 40320
    \item 30 days - 172800
\end{itemize}

In this calculation we will use reward amount for Arcturus and Oldenburg eras where 1.5 OCTA from each block going to staking fund.

The total amount of coins mined for 1 week would be 60480 OCTA.

Let’s assume we have 10 nodes up and running, then the 60480 OCTA would be distributed across they in the following proportion:

\begin{itemize}
    \item 60\% (base reward) - 36240 OCTA, 3624 for each node
    \item 20\% (gpu reward) - 12080 OCTA, 1208 for each node which provide renting service with GPU
    \item 10\% (vpn reward) - 6040 OCTA, 604 for each node which provide VPN service
    \item 10\% (rent reward) - 6040 OCTA, 604 for each node which provide renting service
\end{itemize}

In case of no nodes for which needs to distribute 40\% (except base reward) the coins will be left in staking fund for the next round.

Most profitable variant is to have node with GPU and which provides both services.
Such node will be rewarded by 6040 OCTA per week and also additional payments for services usage.

Due to the current scheme, we can calculate minimal monthly ROI in the following way:

\[
    ROI = \frac{MonthReward / Collateral * 100}{N} = \frac{M}{100} * 60
\]

Where \textbf{MonthReward} is 172800 blocks multiply by staking reward according to current era.

\textbf{N} is amount of nodes participated in staking, for example 10.

Therefore the minimal ROI for Arcturus and Oldenburg eras will be:

\[
    ROI = \frac{172800 / 100000 * 100}{10} = \frac{17.28}{100} * 60 = 10.36\%
\]
